---
title: "Data Manipulation Visualization on Diamonds Dataset"
output: rmarkdown::github_document
---

# About Data
Prices of 50,000 round cut diamonds

Description: A dataset containing the prices and other attributes of almost 54,000 diamonds. The variables are as follows:

Usage: diamonds

Format: A data frame with 53940 rows and 10 variables:

* price: price in US dollars (\$326–\$18,823)
* carat: weight of the diamond (0.2–5.01)
* cut: quality of the cut (Fair, Good, Very Good, Premium, Ideal)
* color: diamond colour, from J (worst) to D (best)
* clarity: a measurement of how clear the diamond is (I1 (worst), SI1, SI2, VS1, VS2, VVS1, VVS2, IF (best))
* x: length in mm (0–10.74)
* y: width in mm (0–58.9)
* z: depth in mm (0–31.8)
* depth: total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43–79)
* table: width of top of diamond relative to widest point (43–95)

```{r, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.path = "README_figs/README-")

library(ggplot2)
library(dplyr)
```

# Ideal Cut Diamomds
## Filter function of Dplyer for data manipulation
```{r, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.path = "README_figs/README-")
diamonds %>% filter(cut == "Ideal") -> Ideal_cut
Ideal_cut %>% filter(price>15000) -> high_price
Ideal_cut %>% filter(price>10000 & price<15000) -> medium_price
Ideal_cut %>% filter(price<10000) -> low_price
```

# Diamond Dimensions
## Select function of dplyer
```{r, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.path = "README_figs/README-")
diamonds %>% select('x','y','z') -> diamond_dimensions
diamond_dimensions %>% filter(x>5 & y>50)
head(diamond_dimensions)
```

# Diamond Color
## Summarize function of dplyer
```{r, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.path = "README_figs/README-")
diamonds %>% filter(color == "D") -> diamond_best_color
diamond_best_color %>% filter(clarity == "IF") -> diamond_best_clarity
diamond_best_clarity %>% summarise(mean_price = mean(price))
head(diamond_dimensions)
```

# Visualization

## Univariate Distribution of Cut with BarPlot
```{r, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.path = "README_figs/README-")
ggplot(data = diamonds, aes(x = cut)) + geom_bar(fill = "lightsalmon3") #all bars with same color
```
```{r, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.path = "README_figs/README-")
ggplot(data =diamonds, aes(x= cut, fill=cut)) + geom_bar() #all bars with different color
```

## Bivariate Analysis - Price vs Carat & Price vs Length of diamond with scatter plot

As carat size increases price of diamonds increases.
```{r, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.path = "README_figs/README-")
ggplot(data =diamonds, aes(y=price, x= carat)) + geom_point(col ="palegreen4") 
```

As length of diamond increases price of diamonds increases.
```{r, echo = FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.path = "README_figs/README-")
ggplot(data =diamonds, aes(y=price, x= x)) + geom_point(col ="mediumorchid4") 
```





